---
title: "Tables for MS"
author: "D. Craven et al."
date: "Sept. 2018"
output: 
  word_document: 
    fig_caption: yes
    fig_height: 6
    highlight: monochrome
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(knitr,quietly = TRUE)
require(dplyr,quietly = TRUE)
require(tidyr, quietly=TRUE)

```

**Table 1.**  Summary of number of plots, sampled area, and environmental conditions across forest plots in the Hawaiian archipelago.   
```{r, echo=FALSE}

haw_study<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen1_Natives_EnvConditions.csv")

haw_study$geo_entity2<-factor(haw_study$geo_entity2, levels=c("Hawai'i Island","Maui Nui", "O'ahu Island", "Kaua'i Island"))


haw_study$totPlotArea<-round(haw_study$totPlotArea, digits=0)
haw_study$mean_MAT<-round(haw_study$mean_MAT, digits=1)
haw_study$mean_MAP<-round(haw_study$mean_MAP, digits=0)
haw_study$mean_PET<-round(haw_study$mean_PET, digits=0)
haw_study$r_PET<-round(haw_study$r_PET, digits=0)
haw_study$max_Elev<-round(haw_study$max_Elev, digits=0)


haw_study<-select(haw_study, "Islands"=geo_entity2,"Plots (#)"=PlotN, "Sampled area (m2)"=totPlotArea, "Individuals (#)"= Abundance_tot_raw, 
                  "MAT (C)"=mean_MAT, "MAP (mm yr-1)"=mean_MAP, "PET (mm yr-1)"=mean_PET, "PET range"=r_PET,"Max. elevation (m)"=max_Elev)
haw_study<-arrange(haw_study, Islands)

haw_study<-kable(haw_study,format="markdown",align="c",digits=1, caption="Table 1.  Summary of number of plots, sampled area, and environmental conditions across forest plots in the Hawaiian archipelago.")
haw_study

```


**Table 2.** Sampled area, number of plots, and number of individuals and species per island across the Hawaiian archipelago (7 plots).      
```{r, echo=FALSE}

std<- function(x,y,z){
    SE<-x/sqrt(y) # standard error
    E<-qt(0.975,df=y-1)*SE
    low_95<-z-E
    hi_95<-z+E
    CIs<-list(low_95,hi_95)
    return(CIs)
}

haw_scen2<-read.table("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen2_Natives_7plots_Envconditions_summarized.csv",sep=",",header=T)
haw_scen2<-select(haw_scen2, geo_entity2, "PlotArea_Scen2"=m_PlotArea,sd_PlotArea,"meanPET_scen2"=mean_PET, "rangePET_scen2"=r_PET)

haw_scen2$n<-100
CIs_2<-std(haw_scen2$sd_PlotArea,haw_scen2$n,haw_scen2$PlotArea_Scen2)
haw_scen2<-cbind.data.frame(haw_scen2,CIs_2[1],CIs_2[2])
colnames(haw_scen2)[7]<-"PlotArea_loCI_Scen2"
colnames(haw_scen2)[8]<-"PlotArea_hiCI_Scen2"

haw_scen2<-select(haw_scen2, geo_entity2,PlotArea_Scen2,PlotArea_loCI_Scen2,PlotArea_hiCI_Scen2, meanPET_scen2,rangePET_scen2)


haw_scen3<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen3_Native_7plots_EnvConditions_summarized.csv",sep=",",header=T)
haw_scen3<-select(haw_scen3, geo_entity2, "PlotArea_Scen3"=m_PlotArea,sd_PlotArea,"meanPET_scen3"=mean_PET, "rangePET_scen3"=r_PET)
haw_scen3$n<-100
CIs_3<-std(haw_scen3$sd_PlotArea,haw_scen3$n,haw_scen3$PlotArea_Scen3)
haw_scen3<-cbind.data.frame(haw_scen3,CIs_3[1],CIs_3[2])
colnames(haw_scen3)[7]<-"PlotArea_loCI_Scen3"
colnames(haw_scen3)[8]<-"PlotArea_hiCI_Scen3"

haw_scen3<-select(haw_scen3, geo_entity2,PlotArea_Scen3,PlotArea_loCI_Scen3,PlotArea_hiCI_Scen3, meanPET_scen3,rangePET_scen3)

haw_scenn<-left_join(haw_scen2,haw_scen3,by="geo_entity2")

haw_scenn$geo_entity2<-factor(haw_scenn$geo_entity2, levels=c("Hawai'i Island","Maui Nui", "O'ahu Island", "Kaua'i Island"))

haw_scenn$PlotArea_Scen2<-round(haw_scenn$PlotArea_Scen2, digits=0)
haw_scenn$PlotArea_loCI_Scen2<-round(haw_scenn$PlotArea_loCI_Scen2, digits=0)
haw_scenn$PlotArea_hiCI_Scen2<-round(haw_scenn$PlotArea_hiCI_Scen2, digits=0)

haw_scenn$PlotArea_Scen2<-paste(haw_scenn$PlotArea_Scen2, "(",haw_scenn$PlotArea_loCI_Scen2,",",haw_scenn$PlotArea_hiCI_Scen2,")")

haw_scenn$meanPET_scen2<-round(haw_scenn$meanPET_scen2, digits=0)
haw_scenn$rangePET_scen2<-round(haw_scenn$rangePET_scen2, digits=0)


haw_scenn$PlotArea_Scen3<-round(haw_scenn$PlotArea_Scen3, digits=0)
haw_scenn$PlotArea_loCI_Scen3<-round(haw_scenn$PlotArea_loCI_Scen3, digits=0)
haw_scenn$PlotArea_hiCI_Scen3<-round(haw_scenn$PlotArea_hiCI_Scen3, digits=0)
haw_scenn$PlotArea_Scen3<-paste(haw_scenn$PlotArea_Scen3, "(",haw_scenn$PlotArea_loCI_Scen3,",",haw_scenn$PlotArea_hiCI_Scen3,")")

haw_scenn$meanPET_scen3<-round(haw_scenn$meanPET_scen3, digits=0)
haw_scenn$rangePET_scen3<-round(haw_scenn$rangePET_scen3, digits=0)

haw_scenn<-select(haw_scenn, geo_entity2, PlotArea_Scen2, meanPET_scen2, rangePET_scen2,PlotArea_Scen3, meanPET_scen3,rangePET_scen3)
haw_scenn<-arrange(haw_scenn, geo_entity2)

haw_scenn<-kable(haw_scenn,format="markdown",align="c",digits=1, caption="Table 2. Summary of sampled area and the range and mean of PET for each sampling scenario across forest plots in the Hawaiian archipelago.")
haw_scenn


```

**Table 3.** Sampled area, number of plots, and number of individuals and species per island across the Hawaiian archipelago (5 plots). 

```{r, echo=FALSE}
std<- function(x,y,z){
    SE<-x/sqrt(y) # standard error
    E<-qt(0.975,df=y-1)*SE
    low_95<-z-E
    hi_95<-z+E
    CIs<-list(low_95,hi_95)
    return(CIs)
}

haw_scen2<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen2_Natives_5plots_Envconditions_summarized.csv")

haw_scen2<-select(haw_scen2, geo_entity2, "PlotArea_Scen2"=m_PlotArea,sd_PlotArea,"meanPET_scen2"=mean_PET, "rangePET_scen2"=r_PET)

haw_scen2$n<-100
CIs_2<-std(haw_scen2$sd_PlotArea,haw_scen2$n,haw_scen2$PlotArea_Scen2)
haw_scen2<-cbind.data.frame(haw_scen2,CIs_2[1],CIs_2[2])
colnames(haw_scen2)[7]<-"PlotArea_loCI_Scen2"
colnames(haw_scen2)[8]<-"PlotArea_hiCI_Scen2"

haw_scen2<-select(haw_scen2, geo_entity2,PlotArea_Scen2,PlotArea_loCI_Scen2,PlotArea_hiCI_Scen2, meanPET_scen2,rangePET_scen2)

haw_scen3<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen3_Native_5plots_EnvConditions_summarized.csv",sep=",",header=T)
haw_scen3<-select(haw_scen3, geo_entity2, "PlotArea_Scen3"=m_PlotArea,sd_PlotArea,"meanPET_scen3"=mean_PET, "rangePET_scen3"=r_PET)
haw_scen3$n<-100
CIs_3<-std(haw_scen3$sd_PlotArea,haw_scen3$n,haw_scen3$PlotArea_Scen3)
haw_scen3<-cbind.data.frame(haw_scen3,CIs_3[1],CIs_3[2])
colnames(haw_scen3)[7]<-"PlotArea_loCI_Scen3"
colnames(haw_scen3)[8]<-"PlotArea_hiCI_Scen3"

haw_scen3<-select(haw_scen3, geo_entity2,PlotArea_Scen3,PlotArea_loCI_Scen3,PlotArea_hiCI_Scen3, meanPET_scen3,rangePET_scen3)

haw_scenn<-left_join(haw_scen2,haw_scen3,by="geo_entity2")

haw_scenn$PlotArea_Scen2<-round(haw_scenn$PlotArea_Scen2, digits=0)
haw_scenn$PlotArea_loCI_Scen2<-round(haw_scenn$PlotArea_loCI_Scen2, digits=0)
haw_scenn$PlotArea_hiCI_Scen2<-round(haw_scenn$PlotArea_hiCI_Scen2, digits=0)

haw_scenn$PlotArea_Scen2<-paste(haw_scenn$PlotArea_Scen2, "(",haw_scenn$PlotArea_loCI_Scen2,",",haw_scenn$PlotArea_hiCI_Scen2,")")

haw_scenn$meanPET_scen2<-round(haw_scenn$meanPET_scen2, digits=0)
haw_scenn$rangePET_scen2<-round(haw_scenn$rangePET_scen2, digits=0)


haw_scenn$PlotArea_Scen3<-round(haw_scenn$PlotArea_Scen3, digits=0)
haw_scenn$PlotArea_loCI_Scen3<-round(haw_scenn$PlotArea_loCI_Scen3, digits=0)
haw_scenn$PlotArea_hiCI_Scen3<-round(haw_scenn$PlotArea_hiCI_Scen3, digits=0)
haw_scenn$PlotArea_Scen3<-paste(haw_scenn$PlotArea_Scen3, "(",haw_scenn$PlotArea_loCI_Scen3,",",haw_scenn$PlotArea_hiCI_Scen3,")")

haw_scenn$meanPET_scen3<-round(haw_scenn$meanPET_scen3, digits=0)
haw_scenn$rangePET_scen3<-round(haw_scenn$rangePET_scen3, digits=0)

haw_scenn<-select(haw_scenn, geo_entity2, PlotArea_Scen2, meanPET_scen2, rangePET_scen2,PlotArea_Scen3, meanPET_scen3,rangePET_scen3)
haw_scenn$geo_entity2<-factor(haw_scenn$geo_entity2, levels=c("Hawai'i Island","Maui Nui", "O'ahu Island", "Kaua'i Island"))
haw_scenn<-arrange(haw_scenn, geo_entity2)

haw_scenn<-kable(haw_scenn,format="markdown",align="c",digits=1, caption="Table 3. Summary of sampled area and the range and mean of PET for each sampling scenario across forest plots in the Hawaiian archipelago (5 plots).")
haw_scenn
```

**Table 4.** Sampled area, number of plots, and number of individuals and species per island across the Hawaiian archipelago (9 plots). 

```{r, echo=FALSE}

std<- function(x,y,z){
    SE<-x/sqrt(y) # standard error
    E<-qt(0.975,df=y-1)*SE
    low_95<-z-E
    hi_95<-z+E
    CIs<-list(low_95,hi_95)
    return(CIs)
}


haw_scen2<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen2_Natives_9plots_Envconditions_summarized.csv")

haw_scen2<-select(haw_scen2, geo_entity2, "PlotArea_Scen2"=m_PlotArea,sd_PlotArea,"meanPET_scen2"=mean_PET, "rangePET_scen2"=r_PET)

haw_scen2$n<-100
CIs_2<-std(haw_scen2$sd_PlotArea,haw_scen2$n,haw_scen2$PlotArea_Scen2)
haw_scen2<-cbind.data.frame(haw_scen2,CIs_2[1],CIs_2[2])
colnames(haw_scen2)[7]<-"PlotArea_loCI_Scen2"
colnames(haw_scen2)[8]<-"PlotArea_hiCI_Scen2"

haw_scen2<-select(haw_scen2, geo_entity2,PlotArea_Scen2,PlotArea_loCI_Scen2,PlotArea_hiCI_Scen2, meanPET_scen2,rangePET_scen2)


haw_scen3<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen3_Native_9plots_EnvConditions_summarized.csv",sep=",",header=T)

haw_scen3<-select(haw_scen3, geo_entity2, "PlotArea_Scen3"=m_PlotArea,sd_PlotArea,"meanPET_scen3"=mean_PET, "rangePET_scen3"=r_PET)
haw_scen3$n<-100
CIs_3<-std(haw_scen3$sd_PlotArea,haw_scen3$n,haw_scen3$PlotArea_Scen3)
haw_scen3<-cbind.data.frame(haw_scen3,CIs_3[1],CIs_3[2])
colnames(haw_scen3)[7]<-"PlotArea_loCI_Scen3"
colnames(haw_scen3)[8]<-"PlotArea_hiCI_Scen3"

haw_scen3<-select(haw_scen3, geo_entity2,PlotArea_Scen3,PlotArea_loCI_Scen3,PlotArea_hiCI_Scen3, meanPET_scen3,rangePET_scen3)

haw_scenn<-left_join(haw_scen2,haw_scen3,by="geo_entity2")

haw_scenn$PlotArea_Scen2<-round(haw_scenn$PlotArea_Scen2, digits=0)
haw_scenn$PlotArea_loCI_Scen2<-round(haw_scenn$PlotArea_loCI_Scen2, digits=0)
haw_scenn$PlotArea_hiCI_Scen2<-round(haw_scenn$PlotArea_hiCI_Scen2, digits=0)

haw_scenn$PlotArea_Scen2<-paste(haw_scenn$PlotArea_Scen2, "(",haw_scenn$PlotArea_loCI_Scen2,",",haw_scenn$PlotArea_hiCI_Scen2,")")

haw_scenn$meanPET_scen2<-round(haw_scenn$meanPET_scen2, digits=0)
haw_scenn$rangePET_scen2<-round(haw_scenn$rangePET_scen2, digits=0)


haw_scenn$PlotArea_Scen3<-round(haw_scenn$PlotArea_Scen3, digits=0)
haw_scenn$PlotArea_loCI_Scen3<-round(haw_scenn$PlotArea_loCI_Scen3, digits=0)
haw_scenn$PlotArea_hiCI_Scen3<-round(haw_scenn$PlotArea_hiCI_Scen3, digits=0)
haw_scenn$PlotArea_Scen3<-paste(haw_scenn$PlotArea_Scen3, "(",haw_scenn$PlotArea_loCI_Scen3,",",haw_scenn$PlotArea_hiCI_Scen3,")")

haw_scenn$meanPET_scen3<-round(haw_scenn$meanPET_scen3, digits=0)
haw_scenn$rangePET_scen3<-round(haw_scenn$rangePET_scen3, digits=0)

haw_scenn<-select(haw_scenn, geo_entity2, PlotArea_Scen2, meanPET_scen2, rangePET_scen2,PlotArea_Scen3, meanPET_scen3,rangePET_scen3)
haw_scenn$geo_entity2<-factor(haw_scenn$geo_entity2, levels=c("Hawai'i Island","Maui Nui", "O'ahu Island", "Kaua'i Island"))
haw_scenn<-arrange(haw_scenn, geo_entity2)

haw_scenn<-kable(haw_scenn,format="markdown",align="c",digits=1, caption="Table 3. Summary of sampled area and the range and mean of PET for each sampling scenario across forest plots in the Hawaiian archipelago (5 plots).")
haw_scenn
```