---
title: "Tables for MS"
author: "D. Craven et al."
date: "Dec. 2018"
output: word_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(knitr,quietly = TRUE)
require(dplyr,quietly = TRUE)
require(tidyr, quietly=TRUE)
```

**Table 1.**  Summary of number of plots, sampled area, and environmental conditions across forest plots in the Hawaiian archipelago
 (native & alien).   
```{r, echo=FALSE}
dat<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/HawIslandsAbundance_2SizeClasses_100plus.csv",header=T)

datt<-filter(dat, SizeClass==5) %>%
  filter(., Native_Status=="alien" |Native_Status=="native")

haw_study<-select(datt, PlotID, geo_entity2, Plot_Area, Elev_m, MAT,MAP, PET ) %>%
           distinct(.)

haw_study<-haw_study %>%
           group_by(geo_entity2)%>%
           summarise(totPlotArea=sum(Plot_Area), mean_MAT=mean(MAT), mean_MAP=mean(MAP), mean_PET=mean(PET),min_PET=min(PET), 
           max_PET=max(PET),max_Elev=max(Elev_m), PlotN=length(unique(PlotID)))
haw_study$r_PET<-haw_study$max_PET-haw_study$min_PET

haw_study$geo_entity2<-factor(haw_study$geo_entity2, levels=c("Hawai'i Island","Maui Nui", "O'ahu Island", "Kaua'i Island"))

haw_study$totPlotArea<-round(haw_study$totPlotArea, digits=0)
haw_study$mean_MAT<-round(haw_study$mean_MAT, digits=1)
haw_study$mean_MAP<-round(haw_study$mean_MAP, digits=0)
haw_study$mean_PET<-round(haw_study$mean_PET, digits=0)
haw_study$r_PET<-round(haw_study$r_PET, digits=0)
haw_study$max_Elev<-round(haw_study$max_Elev, digits=0)

inds<-summarise(group_by(datt, geo_entity2), Abundance_tot_raw=sum(Abundance))

haw_study<-left_join(haw_study, inds, by="geo_entity2")

haw_study<-select(haw_study, "Islands"=geo_entity2,"Plots (#)"=PlotN, "Sampled area (m2)"=totPlotArea, "Individuals (#)"= Abundance_tot_raw, 
                  "MAT (C)"=mean_MAT, "MAP (mm yr-1)"=mean_MAP, "PET (mm yr-1)"=mean_PET, "PET range"=r_PET,"Max. elevation (m)"=max_Elev)

haw_study<-arrange(haw_study, Islands)

haw_study<-kable(haw_study,format="markdown",align="c",digits=1, caption="Table 1.  Summary of number of plots, sampled area, and environmental conditions across forest plots in the Hawaiian archipelago.")
haw_study

```


**Table 2.** Sampled area, number of plots, and number of individuals and species per island across the Hawaiian archipelago (10 plots; native species; both sampling scenarios).      
```{r, echo=FALSE}

std<- function(x,y,z){
  SE<-x/sqrt(y) # standard error
  E<-qt(0.975,df=y-1)*SE
  low_95<-z-E
  hi_95<-z+E
  CIs<-list(low_95,hi_95)
  return(CIs)
}

haw_scen2<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen2_Natives_10plots_Envconditions_summarized.csv",header=T)
haw_scen2<-select(haw_scen2, geo_entity2, "PlotArea_Scen2"=m_PlotArea,sd_PlotArea,"meanPET_scen2"=mean_PET, "rangePET_scen2"=r_PET)

haw_scen2$n<-100
CIs_2<-std(haw_scen2$sd_PlotArea,haw_scen2$n,haw_scen2$PlotArea_Scen2)
haw_scen2<-cbind.data.frame(haw_scen2,CIs_2[1],CIs_2[2])
colnames(haw_scen2)[7]<-"PlotArea_loCI_Scen2"
colnames(haw_scen2)[8]<-"PlotArea_hiCI_Scen2"

haw_scen2<-select(haw_scen2, geo_entity2,PlotArea_Scen2,PlotArea_loCI_Scen2,PlotArea_hiCI_Scen2, meanPET_scen2,rangePET_scen2)

haw_scen3<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen3_Native_10plots_EnvConditions_summarized.csv",sep=",",header=T)
haw_scen3<-select(haw_scen3, geo_entity2, "PlotArea_Scen3"=m_PlotArea,sd_PlotArea,"meanPET_scen3"=mean_PET, "rangePET_scen3"=r_PET)
haw_scen3$n<-100
CIs_3<-std(haw_scen3$sd_PlotArea,haw_scen3$n,haw_scen3$PlotArea_Scen3)
haw_scen3<-cbind.data.frame(haw_scen3,CIs_3[1],CIs_3[2])
colnames(haw_scen3)[7]<-"PlotArea_loCI_Scen3"
colnames(haw_scen3)[8]<-"PlotArea_hiCI_Scen3"

haw_scen3<-select(haw_scen3, geo_entity2,PlotArea_Scen3,PlotArea_loCI_Scen3,PlotArea_hiCI_Scen3, meanPET_scen3,rangePET_scen3)

haw_scenn<-left_join(haw_scen2,haw_scen3,by="geo_entity2")

haw_scenn$geo_entity2<-factor(haw_scenn$geo_entity2, levels=c("Hawai'i Island","Maui Nui", "O'ahu Island", "Kaua'i Island"))

haw_scenn$PlotArea_Scen2<-round(haw_scenn$PlotArea_Scen2, digits=0)
haw_scenn$PlotArea_loCI_Scen2<-round(haw_scenn$PlotArea_loCI_Scen2, digits=0)
haw_scenn$PlotArea_hiCI_Scen2<-round(haw_scenn$PlotArea_hiCI_Scen2, digits=0)

haw_scenn$PlotArea_Scen2<-paste(haw_scenn$PlotArea_Scen2, "(",haw_scenn$PlotArea_loCI_Scen2,",",haw_scenn$PlotArea_hiCI_Scen2,")")

haw_scenn$meanPET_scen2<-round(haw_scenn$meanPET_scen2, digits=0)
haw_scenn$rangePET_scen2<-round(haw_scenn$rangePET_scen2, digits=0)

haw_scenn$PlotArea_Scen3<-round(haw_scenn$PlotArea_Scen3, digits=0)
haw_scenn$PlotArea_loCI_Scen3<-round(haw_scenn$PlotArea_loCI_Scen3, digits=0)
haw_scenn$PlotArea_hiCI_Scen3<-round(haw_scenn$PlotArea_hiCI_Scen3, digits=0)
haw_scenn$PlotArea_Scen3<-paste(haw_scenn$PlotArea_Scen3, "(",haw_scenn$PlotArea_loCI_Scen3,",",haw_scenn$PlotArea_hiCI_Scen3,")")

haw_scenn$meanPET_scen3<-round(haw_scenn$meanPET_scen3, digits=0)
haw_scenn$rangePET_scen3<-round(haw_scenn$rangePET_scen3, digits=0)

haw_scenn<-select(haw_scenn, geo_entity2, PlotArea_Scen2, meanPET_scen2, rangePET_scen2,PlotArea_Scen3, meanPET_scen3,rangePET_scen3)
haw_scenn<-arrange(haw_scenn, geo_entity2)

haw_scenn<-kable(haw_scenn,format="markdown",align="c",digits=1, caption="Table 2. Summary of sampled area and the range and mean of PET for each sampling scenario across forest plots in the Hawaiian archipelago (just native species).")
haw_scenn


```

**Table 3.** Sampled area, number of plots, and number of individuals and species per island across the Hawaiian archipelago (10 plots; native & alien species; both sampling scenarios).      
```{r, echo=FALSE}

std<- function(x,y,z){
  SE<-x/sqrt(y) # standard error
  E<-qt(0.975,df=y-1)*SE
  low_95<-z-E
  hi_95<-z+E
  CIs<-list(low_95,hi_95)
  return(CIs)
}

haw_scen2<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen2_Total_10plots_Envconditions_summarized.csv",header=T)
haw_scen2<-select(haw_scen2, geo_entity2, "PlotArea_Scen2"=m_PlotArea,sd_PlotArea,"meanPET_scen2"=mean_PET, "rangePET_scen2"=r_PET)

haw_scen2$n<-100
CIs_2<-std(haw_scen2$sd_PlotArea,haw_scen2$n,haw_scen2$PlotArea_Scen2)
haw_scen2<-cbind.data.frame(haw_scen2,CIs_2[1],CIs_2[2])
colnames(haw_scen2)[7]<-"PlotArea_loCI_Scen2"
colnames(haw_scen2)[8]<-"PlotArea_hiCI_Scen2"

haw_scen2<-select(haw_scen2, geo_entity2,PlotArea_Scen2,PlotArea_loCI_Scen2,PlotArea_hiCI_Scen2, meanPET_scen2,rangePET_scen2)

haw_scen3<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen3_Total_10plots_EnvConditions_summarized.csv",sep=",",header=T)
haw_scen3<-select(haw_scen3, geo_entity2, "PlotArea_Scen3"=m_PlotArea,sd_PlotArea,"meanPET_scen3"=mean_PET, "rangePET_scen3"=r_PET)
haw_scen3$n<-100
CIs_3<-std(haw_scen3$sd_PlotArea,haw_scen3$n,haw_scen3$PlotArea_Scen3)
haw_scen3<-cbind.data.frame(haw_scen3,CIs_3[1],CIs_3[2])
colnames(haw_scen3)[7]<-"PlotArea_loCI_Scen3"
colnames(haw_scen3)[8]<-"PlotArea_hiCI_Scen3"

haw_scen3<-select(haw_scen3, geo_entity2,PlotArea_Scen3,PlotArea_loCI_Scen3,PlotArea_hiCI_Scen3, meanPET_scen3,rangePET_scen3)

haw_scenn<-left_join(haw_scen2,haw_scen3,by="geo_entity2")

haw_scenn$geo_entity2<-factor(haw_scenn$geo_entity2, levels=c("Hawai'i Island","Maui Nui", "O'ahu Island", "Kaua'i Island"))

haw_scenn$PlotArea_Scen2<-round(haw_scenn$PlotArea_Scen2, digits=0)
haw_scenn$PlotArea_loCI_Scen2<-round(haw_scenn$PlotArea_loCI_Scen2, digits=0)
haw_scenn$PlotArea_hiCI_Scen2<-round(haw_scenn$PlotArea_hiCI_Scen2, digits=0)

haw_scenn$PlotArea_Scen2<-paste(haw_scenn$PlotArea_Scen2, "(",haw_scenn$PlotArea_loCI_Scen2,",",haw_scenn$PlotArea_hiCI_Scen2,")")

haw_scenn$meanPET_scen2<-round(haw_scenn$meanPET_scen2, digits=0)
haw_scenn$rangePET_scen2<-round(haw_scenn$rangePET_scen2, digits=0)

haw_scenn$PlotArea_Scen3<-round(haw_scenn$PlotArea_Scen3, digits=0)
haw_scenn$PlotArea_loCI_Scen3<-round(haw_scenn$PlotArea_loCI_Scen3, digits=0)
haw_scenn$PlotArea_hiCI_Scen3<-round(haw_scenn$PlotArea_hiCI_Scen3, digits=0)
haw_scenn$PlotArea_Scen3<-paste(haw_scenn$PlotArea_Scen3, "(",haw_scenn$PlotArea_loCI_Scen3,",",haw_scenn$PlotArea_hiCI_Scen3,")")

haw_scenn$meanPET_scen3<-round(haw_scenn$meanPET_scen3, digits=0)
haw_scenn$rangePET_scen3<-round(haw_scenn$rangePET_scen3, digits=0)

haw_scenn<-select(haw_scenn, geo_entity2, PlotArea_Scen2, meanPET_scen2, rangePET_scen2,PlotArea_Scen3, meanPET_scen3,rangePET_scen3)
haw_scenn<-arrange(haw_scenn, geo_entity2)

haw_scenn<-kable(haw_scenn,format="markdown",align="c",digits=1, caption="Table 3. Summary of sampled area and the range and mean of PET for each sampling scenario across forest plots in the Hawaiian archipelago (native & alien species).")
haw_scenn
```

**Table 3.** Sampled area, number of plots, and number of individuals and species per island across the Hawaiian archipelago (10 plots; only alien species; both sampling scenarios).      
```{r, echo=FALSE}

std<- function(x,y,z){
  SE<-x/sqrt(y) # standard error
  E<-qt(0.975,df=y-1)*SE
  low_95<-z-E
  hi_95<-z+E
  CIs<-list(low_95,hi_95)
  return(CIs)
}

haw_scen2<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen2_Aliens_10plots_Envconditions_summarized.csv",header=T)
haw_scen2<-select(haw_scen2, geo_entity2, "PlotArea_Scen2"=m_PlotArea,sd_PlotArea,"meanPET_scen2"=mean_PET, "rangePET_scen2"=r_PET)

haw_scen2$n<-100
CIs_2<-std(haw_scen2$sd_PlotArea,haw_scen2$n,haw_scen2$PlotArea_Scen2)
haw_scen2<-cbind.data.frame(haw_scen2,CIs_2[1],CIs_2[2])
colnames(haw_scen2)[7]<-"PlotArea_loCI_Scen2"
colnames(haw_scen2)[8]<-"PlotArea_hiCI_Scen2"

haw_scen2<-select(haw_scen2, geo_entity2,PlotArea_Scen2,PlotArea_loCI_Scen2,PlotArea_hiCI_Scen2, meanPET_scen2,rangePET_scen2)

haw_scen3<-read.csv("/home/dylan/Dropbox (iDiv)/Research_projects/Veg. monitoring databases/databases and field protocols/database/IslandForests/Hawaii_only/Diversity_Age/Hawaii_diversity/Cleaned_Data/Scen3_Aliens_10plots_EnvConditions_summarized.csv",sep=",",header=T)
haw_scen3<-select(haw_scen3, geo_entity2, "PlotArea_Scen3"=m_PlotArea,sd_PlotArea,"meanPET_scen3"=mean_PET, "rangePET_scen3"=r_PET)
haw_scen3$n<-100
CIs_3<-std(haw_scen3$sd_PlotArea,haw_scen3$n,haw_scen3$PlotArea_Scen3)
haw_scen3<-cbind.data.frame(haw_scen3,CIs_3[1],CIs_3[2])
colnames(haw_scen3)[7]<-"PlotArea_loCI_Scen3"
colnames(haw_scen3)[8]<-"PlotArea_hiCI_Scen3"

haw_scen3<-select(haw_scen3, geo_entity2,PlotArea_Scen3,PlotArea_loCI_Scen3,PlotArea_hiCI_Scen3, meanPET_scen3,rangePET_scen3)

haw_scenn<-left_join(haw_scen2,haw_scen3,by="geo_entity2")

haw_scenn$geo_entity2<-factor(haw_scenn$geo_entity2, levels=c("Hawai'i Island","Maui Nui", "O'ahu Island", "Kaua'i Island"))

haw_scenn$PlotArea_Scen2<-round(haw_scenn$PlotArea_Scen2, digits=0)
haw_scenn$PlotArea_loCI_Scen2<-round(haw_scenn$PlotArea_loCI_Scen2, digits=0)
haw_scenn$PlotArea_hiCI_Scen2<-round(haw_scenn$PlotArea_hiCI_Scen2, digits=0)

haw_scenn$PlotArea_Scen2<-paste(haw_scenn$PlotArea_Scen2, "(",haw_scenn$PlotArea_loCI_Scen2,",",haw_scenn$PlotArea_hiCI_Scen2,")")

haw_scenn$meanPET_scen2<-round(haw_scenn$meanPET_scen2, digits=0)
haw_scenn$rangePET_scen2<-round(haw_scenn$rangePET_scen2, digits=0)

haw_scenn$PlotArea_Scen3<-round(haw_scenn$PlotArea_Scen3, digits=0)
haw_scenn$PlotArea_loCI_Scen3<-round(haw_scenn$PlotArea_loCI_Scen3, digits=0)
haw_scenn$PlotArea_hiCI_Scen3<-round(haw_scenn$PlotArea_hiCI_Scen3, digits=0)
haw_scenn$PlotArea_Scen3<-paste(haw_scenn$PlotArea_Scen3, "(",haw_scenn$PlotArea_loCI_Scen3,",",haw_scenn$PlotArea_hiCI_Scen3,")")

haw_scenn$meanPET_scen3<-round(haw_scenn$meanPET_scen3, digits=0)
haw_scenn$rangePET_scen3<-round(haw_scenn$rangePET_scen3, digits=0)

haw_scenn<-select(haw_scenn, geo_entity2, PlotArea_Scen2, meanPET_scen2, rangePET_scen2,PlotArea_Scen3, meanPET_scen3,rangePET_scen3)
haw_scenn<-arrange(haw_scenn, geo_entity2)

haw_scenn<-kable(haw_scenn,format="markdown",align="c",digits=1, caption="Table 3. Summary of sampled area and the range and mean of PET for each sampling scenario across forest plots in the Hawaiian archipelago (native & alien species).")
haw_scenn
```